An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2022-02-07 latex_files/ch3/3-0-design-principles.tex
addressed henri's comments

For designing an extendable implementation of ROMC, we firstly define
ROMC as a sequence of algorithmic steps. The algorithmic view of ROMC
serves as the driver for the implementation at \pkg{ELFI}. At a high
level, ROMC can be split into the training and the inference part. In
general terms, the training part covers all steps for estimating the
proposal regions and the inference part for getting weighted
samples. Algorithm~\ref{alg:romc_algorithm} defines ROMC formally;
Steps 2-10 (before the vertical line) form the training part, while
steps 12-17 the inference part.

\begin{algorithm}[!ht]
	\caption{ROMC}\label{alg:romc_algorithm}
	\begin{algorithmic}[1]
    \Procedure{ROMC}{$M_r(\thetab), n_1, n_2, \epsilon$}
    \For{$i \gets 1 \textrm{ to } n_1$}
      \State $\vb_i \sim p(\vb)$ \Comment{Draw nuisance variables}
      \State $d_i(\thetab) = M_d(\thetab, \vb=\vb_i)$ \Comment{Define distance function}
      \State $\thetab_i^* = \text{argmin}_{\thetab} d_i$, $d_i^*=d_i(\thetab_i^*)$ \Comment{Solve optimization problem}
      \If{$d^*_i > \epsilon$}
        \State Go to 2 \Comment{Filter solution}
      \EndIf
      \State Define $q_i$ over $\mathcal{\hat{S}}$ \Comment{Estimate proposal area}
      \State (Optional) Fit $\Tilde{d}_i$ on $\mathcal{\hat{S}}$ \Comment{Fit surrogate model}
      \\\hrulefill
      \For{$j \gets 1 \textrm{ to } n_2$}      
        \State $\thetab_{ij} \sim q_i$, compute $w_{ij}$ \Comment{Sample}
      \EndFor
    \EndFor
    \State $E_{p(\thetab|\data)}[h(\thetab)]$ \Comment{Estimate an expectation}
    \State $p_{d,\epsilon}(\thetab)$ \Comment{Evaluate the unnormalized posterior}
    \EndProcedure
	\end{algorithmic}
\end{algorithm}

\subsubsection*{Training part}
\noindent
At the training (fitting) part, the goal is the estimation of the
proposal regions $\mathcal{\hat{S}}_i$. The tasks are; (a) sampling
the nuisance variables $\vb_i \sim p(\vb)$ for obtaining the
deterministic functions $d_i(\thetab)$, (b) defining the optimisation
problems $\min_{\thetab} \: d_i(\thetab)$, (c) obtaining
$\thetab_i^*$, $d_i^*$ (d) checking whether $d_i^* \leq \epsilon$ and
(e) computing the proposal distribution $q_i$. If $d_i(\thetab)$ is
differentiable, using a gradient-based method is advised for obtaining
$\thetab_i^*$ faster. In case $\nabla_{\thetab} d_i$ is available in
closed-form, the procedure is upgraded in terms of both accuracy and
efficiency. If closed-form description is not available, gradients
approximation with finite-differences requires two evaluations of
$d_i$ for \emph{each} parameter $\theta_d$, which can only work in
low-dimensional problems. If $d_i(\thetab)$ is not differentiable, the
Bayesian Optimisation can be used as an alternative solution. In this
scenario, the training part becomes slower due to fitting of the
surrogate model and the blind optimisation steps. After obtaning the
optimal points $\thetab^*$, the training part gets completed by
estimating the proposal regions;
Algorithm~\ref{alg:region_construction} describes the line search
approach for finding the region's boundaries.

\subsubsection*{Inference Part}
Performing the inference includes one or more of the following three
tasks; (a) sampling from the posterior
$ \thetab_i \sim p_{d, \epsilon}(\thetab|\data)$, (b) computing an
expectation $E_{\thetab|\data}[h(\thetab)]$ or (c) evaluating the
unnormalised posterior $p_{d, \epsilon}(\thetab|\data)$. Sampling is
performed by getting $n_2$ samples from each proposal distribution
$q_i$. For each sample $\thetab_{ij}$, the distance
function\footnote{As before, if a surrogate model $\hat{d}$ is
  available, it can be utilised as the distance function.} is
evaluated for checking if it lies inside the acceptance
region. Algorithm~\ref{alg:sampling_GB} defines the steps for
computing a weighted sample. Computing an expectation can be done
easily after weighted samples are obtained using the
equation~\ref{eq:expectation}, so we do not discuss it
separately. Evaluating the unnormalised posterior requires the
deterministic functions $g_i$ and the prior distribution
$p(\thetab)$\footnote{There is no need for solving the optimisation
  problems and building the proposal regions.}. The evaluation
requires iterating over all $g_i$ and evaluating the distance from the
observed data.

% \begin{minipage}{0.46\textwidth}
% \begin{algorithm}[H]
%     \centering
%     \caption{Training Part - Gradient-based. Requires $g_i(\thetab), p(\thetab)$}\label{alg:training_GB}
%     \begin{algorithmic}[1]
%       \For{$i \gets 1 \textrm{ to } n$}
%         \State Obtain $\thetab_i^*$ using a Gradient Optimiser
%         \If{$g_i(\thetab_i^*) > \epsilon$}
%         \State{go to} 1
%         \Else
%         \State Approximate $\jac_i^* = \nabla g_i(\theta)$ and $H_i \approx \jac^T_i\jac_i$
%         \State Use Algorithm~\ref{alg:region_construction} to obtain $q_i$
%         \EndIf      
%       \EndFor
%       \Return{$q_i, p(\theta), g_i(\theta)$}
%     \end{algorithmic}
% \end{algorithm}
% \end{minipage}
% \hfill
% \begin{minipage}{0.46\textwidth}
% \begin{algorithm}[H]
%     \centering
%     \caption{Training Part - Bayesian optimisation. Requires $g_i(\thetab), p(\thetab)$}\label{alg:training_GP}
%     \begin{algorithmic}[1]
%       \For{$i \gets 1 \textrm{ to } n$}
%         \State Obtain $\thetab_i^*, \hat{d}_i(\thetab)$ using a GP approach
%         \If{$g_i(\thetab_i^*) > \epsilon$}
%         \State{go to} 1
%         \Else
%         \State Approximate $H_i \approx \jac^T_i \jac_i$
%         \State Use Algorithm~\ref{alg:region_construction} to obtain $q_i$
%         \EndIf      
%       \EndFor
%       \Return{$q_i, p(\theta), \hat{d}_i(\theta)$}
%     \end{algorithmic}
% \end{algorithm}
% \end{minipage}

\begin{algorithm}[!ht]
	\caption{Approximation of $\mathcal{\hat{S}}_i$ with a bounding box; Requires, a model of distance $d_i(\thetab)$, optimal point $\thetab_i^*$, number of refinements $K$, step size $\eta\_\text{start}$, maximum iterations $M$ and curvature matrix $\hessian_i$ ($\jac_i^T\jac_i $ or GP Hessian)}\label{alg:region_construction}
	\begin{algorithmic}[1]
	\State Compute eigenvectors $\vb_{d}$ of $\hess_i$ {\scriptsize ($d = 1,\ldots,||\thetab ||)$}
	\For{$d \gets 1 \textrm{ to } ||\thetab||$}
		\State $\Tilde{\thetab} \gets \thetab_i^*$ \label{algstep:box_constr_start}
		\State $k \gets 0$
		\State $\eta \gets \eta\_\text{start}$ \Comment{Initialize $\eta$}
		\Repeat
          \State $j \gets 0$
        	\Repeat
            \State $\Tilde{\thetab} \gets \Tilde{\thetab} + \eta \ \vb_{d}$ \Comment{Large step size $\eta$.}
            \State $j \gets j + 1$
        	\Until{$d(f_i(\Tilde{\thetab}), \data) > \epsilon$ or $j \geq M$} \Comment{Check distance or maximum iterations}
        	\State $\Tilde{\thetab} \gets \Tilde{\thetab} - \eta \ \vb_{d}$
        	\State $\eta \gets \eta/2$ \Comment{More accurate region boundary}
        	\State $k \gets k + 1$
      \Until $k = K$
      \If{$\Tilde{\thetab} = \thetab_i^*$} \Comment{Check if no step has been done}
        \State $\Tilde{\thetab} \gets \Tilde{\thetab} + \dfrac{\eta\_{\text{start}}}{2^K} \vb_d$ \Comment{Then, make the minimum step}
      \EndIf
    	\State Set final $\Tilde{\thetab}$ as region end point. \label{algstep:box_constr_end}
    	\State Repeat steps~\ref{algstep:box_constr_start}~-~\ref{algstep:box_constr_end} for $\mathbf{v}_{d} = - \mathbf{v}_{d}$
	\EndFor
	\State Fit a rectangular box around the region end points and define $q_i$ as uniform distribution
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
    \centering
    \caption{Sampling. Requires a function of distance $d_i$, the prior distribution $p(\thetab)$, the proposal distribution $q_i$}\label{alg:sampling_GB}
    \begin{algorithmic}[1]
      \State $\thetab_{ij} \sim q_i$
          \If {$d_i(\thetab_{ij}) > \epsilon$}
            \State Go to 2 \Comment{Reject sample}
          \Else {}
            \State $w_{ij} = \frac{p(\thetab_{ij})}{q(\thetab_{ij})}$ \Comment{Compute weight}
            \State Store $(w_{ij}, \thetab_{ij})$ \Comment{Store weighted sample}
          \EndIf
    \end{algorithmic}
\end{algorithm}

>>>>

For designing an extendable implementation of ROMC, we firstly define
ROMC as a sequence of algorithmic steps. The algorithmic view of ROMC
serves as the driver for the implementation at \pkg{ELFI}. At a high
level, ROMC can be split into the training and the inference part. In
general terms, the training part covers all steps for estimating the
proposal regions and the inference part calculates the weighted
samples. Algorithm~\ref{alg:romc_algorithm} defines ROMC formally;
Steps 2-10 (before the horizontal line) form the training part and
steps 12-17 the inference part, respectively.

\begin{algorithm}[!ht]
	\caption{ROMC. Requires the prior \( p(\thetab) \), the simulator
    \(M_r(\thetab)\), number of optimisation problems \(n_1\), number
    of samples per region \(n_2\), acceptance limit
    \(\epsilon\)}\label{alg:romc_algorithm}
	\begin{algorithmic}[1]
    \Procedure{ROMC}{}
    \For{\(i \gets 1 \textrm{ to } n_1\)}
    \State \(\vb_i \sim p(\vb)\) \Comment{Draw nuisance variables}
    \State Convert \(M_r(\thetab) \) to \( g(\thetab, \vb=\vb_i) \) \Comment{Define deterministic simulator}
      \State \( d_i(\thetab) = ||g(\thetab, \vb=\vb_i) - \yb_0||_2 \) \Comment{Define distance function}
      \State \(\thetab_i^* = \text{argmin}_{\thetab} d_i\), \(d_i^*=d_i(\thetab_i^*)\) \Comment{Solve optimisation problem}
      \If{\(d^*_i > \epsilon\)}
        \State Go to 2 \Comment{Filter solution}
      \EndIf
      \State Estimate \(\mathcal{\hat{S}}_i\) and define \(q_i\) \Comment{Estimate proposal area}
      \State (Optional) Fit \(\Tilde{d}_i\) on \(\mathcal{\hat{S}}_i\) \Comment{Fit surrogate model}
      \\\hrulefill
      \For{\(j \gets 1 \textrm{ to } n_2\)}
      \State \(\thetab_{ij} \sim q_i\), compute \(w_{ij}\) as in Algorithm \ref{alg:sampling_GB} \Comment{Sample}
      \EndFor
    \EndFor
    \State \(E_{p(\thetab|\data)}[h(\thetab)]\) as in eq.~\eqref{eq:expectation} \Comment{Estimate an expectation}
    \State \(p_{d,\epsilon}(\thetab) \) as in eq.~\eqref{eq:approx_posterior_omc} \Comment{Evaluate the unnormalised posterior}
    \EndProcedure
	\end{algorithmic}
\end{algorithm}

\subsubsection*{Training part}
\noindent
At the training (fitting) part, the goal is the estimation of the
proposal regions \(\mathcal{\hat{S}}_i\). The tasks are; (a) sampling
the nuisance variables \(\vb_i \sim p(\vb)\) for obtaining the
deterministic functions \(d_i(\thetab)\), (b) defining the optimisation
problems \(\min_{\thetab} \: d_i(\thetab)\), (c) obtaining
\(\thetab_i^*\), \(d_i^*\) (d) checking whether \(d_i^* \leq \epsilon\) and
(e) computing the proposal distribution \(q_i\).

If \(d_i(\thetab)\) is differentiable, using a gradient-based method
is advised for obtaining \(\thetab_i^*\) faster. In this case, the
gradients \(\nabla_{\thetab} d_i\) gradients are approximated
automatically with finite-differences. This approximation requires two
evaluations of \(d_i\) for \emph{each} parameter
\(\theta_d, d \in \{1, \ldots, D\}\)\footnote{\(D\) is the
  dimensionality of \(\thetab\), i.e.  \(\thetab \in \mathbb{R}^D\)},
which works in low-dimensional problems. If \(d_i(\thetab)\) is not
differentiable, Bayesian Optimisation can be used as an alternative
solution. In this scenario, the training part becomes slower due to
fitting of the surrogate model and the blind optimisation steps.

After obtaining the optimal points \(\thetab^*\), we estimate the
proposal regions. Algorithm~\ref{alg:region_construction} describes
the line search approach for finding the region's boundaries. An
important step for the proposal region estimation is deciding the axes
of the bounding box; the directions \(\vb_d, d = \{1, \ldots, D\}\) we
follow for reaching the boundaries. We approximate them as the
direction of the highest curvature of \(d_i\) at \(\thetab_i^*\). This
estimation is given by the eigenvalues of the Hessian matrix
\(\hessian_i\) of \(d_i\)\footnote{Either the real distance \(d_i\) or
  the Gaussian Process approximation \(\hat{d}_i\)} at
\(\thetab_i\). The Hessian matrix is approximated numerically. In case
where the distance function is the Euclidean, the Hessian matrix can
be also computed as \(\hessian_i = \jac_i^T\jac_i\), where \(\jac_i\)
is the Jacobian matrix of the summary statistics
\(\Phi(g(\thetab, \vb=\vb_i))\) at \(\thetab_i^*\). The approximation
through the Jacobian matrix has the computational advantage of using
only first-order derivatives.

\subsubsection*{Inference Part}
Performing the inference includes one or more of the following three
tasks; (a) sampling from the posterior
\( \thetab_i \sim p_{d, \epsilon}(\thetab|\data)\), (b) computing an
expectation \(E_{\thetab|\data}[h(\thetab)]\) and (c) evaluating the
unnormalised posterior \(p_{d, \epsilon}(\thetab|\data)\). Sampling is
performed by getting \(n_2\) samples from each proposal distribution
\(q_i\). For each sample \(\thetab_{ij}\), the distance
function\footnote{As before, if a surrogate model \(\hat{d}\) is
  available, it can be utilised as the distance function.} is
evaluated for checking if it lies inside the acceptance
region. Algorithm~\ref{alg:sampling_GB} defines the steps for
computing a weighted sample. Computing the expectation is easy after
weighted samples are obtained using the equation~\ref{eq:expectation},
so we do not discuss it separately. Evaluating the unnormalised
posterior requires the deterministic functions \(g_i\) and the prior
distribution \(p(\thetab)\)\footnote{There is no need for solving the
  optimisation problems and building the proposal regions.}. The
evaluation requires iterating over all \(g_i\) and evaluating the
distance from the observed data.

\begin{algorithm}[!ht]
	\caption{Approximation of \(\mathcal{\hat{S}}_i\) with a bounding box; 
  Requires: a model of distance \(d_i(\thetab)\), 
  an optimal point \(\thetab_i^*\), 
  a number of refinements \(K\), 
  a step size \(\eta\_\text{start}\), 
  maximum iterations \(M\) and 
  a curvature matrix \(\hessian_i\) (\(\jac_i^T\jac_i \) or GP Hessian)}\label{alg:region_construction}
	\begin{algorithmic}[1]
	\State Compute eigenvectors \(\vb_{d}\) of \(\hess_i\) {\scriptsize (\(d = 1,\ldots,||\thetab ||)\)}
	\For{\(d \gets 1 \textrm{ to } D\)}
		\State \(\Tilde{\thetab} \gets \thetab_i^*\) \label{algstep:box_constr_start}
		\State \(k \gets 0\)
		\State \(\eta \gets \eta\_\text{start}\) \Comment{Initialize \(\eta\)}
		\Repeat
          \State \(j \gets 0\)
        	\Repeat
            \State \(\Tilde{\thetab} \gets \Tilde{\thetab} + \eta \ \vb_{d}\) \Comment{Large step size \(\eta\).}
            \State \(j \gets j + 1\)
        	\Until{\(d(f_i(\Tilde{\thetab}), \data) > \epsilon\) or \(j \geq M\)} \Comment{Check distance or maximum iterations}
        	\State \(\Tilde{\thetab} \gets \Tilde{\thetab} - \eta \ \vb_{d}\)
        	\State \(\eta \gets \eta/2\) \Comment{More accurate region boundary}
        	\State \(k \gets k + 1\)
      \Until \(k = K\)
      \If{\(\Tilde{\thetab} = \thetab_i^*\)} \Comment{Check if no step has been done}
        \State \(\Tilde{\thetab} \gets \Tilde{\thetab} + \dfrac{\eta\_{\text{start}}}{2^K} \vb_d\) \Comment{Then, make the minimum step}
      \EndIf \label{algstep:box_constr_end}
    	\State Set \(\Tilde{\thetab}\) as the positive end point along \(\mathbf{v}_{d}\)
    	\State Repeat steps~\ref{algstep:box_constr_start}~-~\ref{algstep:box_constr_end} for \(\mathbf{v}_{d} = - \mathbf{v}_{d}\) and set \(\Tilde{\thetab}\) as the negative end point along \(\mathbf{v}_{d}\)
	\EndFor
	\State Fit a rectangular box around the region end points and define \(q_i\) as uniform distribution
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
    \centering
    \caption{Sampling. Requires a function of distance \(d_i\), the prior distribution \(p(\thetab)\), the proposal distribution \(q_i\)}\label{alg:sampling_GB}
    \begin{algorithmic}[1]
      \State \(\thetab_{ij} \sim q_i\)
          \If {\(d_i(\thetab_{ij}) > \epsilon\)}
            \State Go to 2 \Comment{Reject sample}
          \Else {}
            \State \(w_{ij} = \frac{p(\thetab_{ij})}{q(\thetab_{ij})}\) \Comment{Compute weight}
            \State Store \((w_{ij}, \thetab_{ij})\) \Comment{Store weighted sample}
          \EndIf
    \end{algorithmic}
\end{algorithm}

### 2022-02-07 latex_files/ch3/3-1-implementation-principles.tex
addressed henri's comments

The overview of our implementation is illustrated in
Figure~\ref{fig:romc_overview}; one may interpret
Figure~\ref{fig:romc_overview} as a depiction of the main class and
the ellipses are the main routines of the class. Following
\proglang{Python}'s naming principles, the methods starting with an
underscore (green ellipses) represent internal (private) functions,
whereas the rest (blue ellipses) are the public methods that the user
interacts with. In Figure~\ref{fig:romc_overview}, it can be easily
observed that the implementation follows consistently Algorithm~\ref{alg:romc_algorithm}. The training part includes
all the steps until the computation of the proposal regions
i.e.~sampling the nuisance variables, defining the optimisation
problems, solving them, constructing the regions and fitting local
surrogate models. The inference part comprises of evaluating the
unnormalised posterior (and the normalised when is possible), sampling
and computing an expectation. We also provide some utilities for
inspecting the training process, such as plotting the histogram of the
final distances or visualising the constructed bounding
boxes. Finally, in the evaluation part, we provide two methods for
evaluating the inference; (a) computing the Effective Sample Size
(ESS) of the samples and (b) measuring the divergence between the
approximate posterior the ground-truth, if the latter is
available.\footnote{Normally, the ground-truth posterior is not
  available; However, this functionality is useful in cases where the
  posterior can be computed numerically or with an alternative method
  (i.e.\ ABC Rejection Sampling), and we would like to measure the
  discrepancy between the two approximations.}

@@

For illustrating the functionalities we will use the following running
example introduced by~\cite{Ikonomov2019}, \textbf{HP comment: what is c in Eq. \eqref{eq:1D_example_eq_2}
and in python snippet? As it is, it will not run. }

@@

The prior is a uniform distribution in the range $[-2.5, 2.5]$ and the
likelihood is defined at~\ref{eq:1D_example_eq_2}. There is only one
observation $y_0 = 0$. The inference in this particular example can be
performed quite easily without using a likelihood-free inference
approach. We can exploit this fact for validating the accuracy of our
implementation.

@@

  def simulator(t1, batch_size=1,random_state=None):
    if t1 < -0.5:
        y = ss.norm(loc=-t1-c, scale=1).rvs(random_state=random_state)
    elif t1 <= 0.5:
        y = ss.norm(loc=t1**4, scale=1).rvs(random_state=random_state)
    else:
        y = ss.norm(loc=t1-c, scale=1).rvs(random_state=random_state)
    return y

>>>>

The overview of our implementation is illustrated in
Figure~\ref{fig:romc_overview}. Following \proglang{Python}'s naming
principles, the methods starting with an underscore (green rectangles)
represent internal (private) functions, whereas the rest (blue
ellipses) are the methods exposed as the public API. In
Figure~\ref{fig:romc_overview}, it can be easily observed that the
implementation follows Algorithm~\ref{alg:romc_algorithm}. The
training part includes all the steps until the computation of the
proposal regions i.e.~sampling the nuisance variables, defining the
optimisation problems, solving them, constructing the regions and
fitting local surrogate models. The inference part comprises of
evaluating the unnormalised posterior (and the normalised when is
possible), sampling and computing an expectation. We also provide some
utilities for inspecting the training process, such as plotting the
histogram of the final distances or visualising the constructed
bounding boxes. Finally, in the evaluation part, we provide two
methods for evaluating the inference; (a) computing the Effective
Sample Size (ESS) of the samples and (b) measuring the divergence
between the approximate posterior the ground-truth, if the latter is
available.\footnote{Normally, the ground-truth posterior is not
  available; However, this functionality is useful in cases where the
  posterior can be computed numerically or with an alternative method
  (i.e.\ ABC Rejection Sampling), and we would like to measure the
  discrepancy between the two approximations.}

@@

For illustrating the functionalities we will use the following running
example introduced by \citet{Ikonomov2019},

@@

The prior is a uniform distribution in the range \([-2.5, 2.5]\) and
the likelihood is defined at~\ref{eq:1D_example_eq_2}. The constant
\(c\) is \(0.5 - 0.5^4\) ensures the continuity of the pdf. There is
only one observation \(y_0 = 0\). The inference in this particular
example can be performed quite easily without using a likelihood-free
inference approach. We can exploit this fact for validating the
accuracy of our implementation.

@@

  def simulator(t1, batch_size=1,random_state=None):
    c = 0.5 - 0.5**4
    if t1 < -0.5:
        y = ss.norm(loc=-t1-c, scale=1).rvs(random_state=random_state)
    elif t1 <= 0.5:
        y = ss.norm(loc=t1**4, scale=1).rvs(random_state=random_state)
    else:
        y = ss.norm(loc=t1-c, scale=1).rvs(random_state=random_state)
    return y

### 2022-02-07 latex_files/ch4/4-1-training.tex
addressed henri's comments

\noindent
This method (a) draws the nuisance variables, (b) defines the
optimisation problems and (c) solves them using either a
gradient-based optimiser or Bayesian optimisation. These tasks are
completed sequentially, as shown in Figure~\ref{fig:romc_overview}. The
definition of the optimisation problems is performed by drawing
\code{n1} integer numbers from a discrete uniform distribution
$u_i \sim \mathcal{U}\{1, 2^{32}-1\}$. Each integer $u_i$ is the seed
used in \pkg{ELFI}'s random simulator. The seeds $u_i$ are
computationally analogous to the random variables $\vb_i$, that were
defined in the previous chapter; setting the \code{seed} eliminates all randomness of the simulator transforming it to a deterministic
function. Setting the argument \code{use_bo=True}, chooses the
Bayesian Optimisation scheme for obtaining $\thetab_i^*$. In this
case, apart from obtaining the optimal points $\thetab_i^*$, we also
fit a GP as a surrogate model $\hat{d}_i$. In this
scenario, in the following steps, $\hat{d}_i(\thetab)$ replaces
$d_i(\thetab)$ as the distance function.

@@

\noindent
This function helps the user decide which threshold $\epsilon$ to
use. It plots a histogram of the distances at the optimal point
$d_i(\thetab_i^*) : \{i = 1, 2, \ldots, n_1\}$ or $\hat{d}_i^*$ in case
\code{use_bo=True}. The function accepts all keyword arguments and
forwards them to the underlying \code{matplotlib.pyplot.hist()} function; in
this way the user may customise some properties of the histogram, such
as the number of bins or the range of values.

@@

\noindent
This method constructs a bounding box around the optimal point
$\thetab_i^* : i = 1, 2, \ldots, n_1$ following
Algorithm~\ref{alg:region_construction}. The Hessian matrix is
approximated based on the Jacobian
$\hess_i = \jac_i^T \jac_i$\footnote{The Jacobian matrix is computed
  on the output of the summary statistics
  $\nabla_{\thetab} \Phi(M_d(\thetab, \vb_i))$ at $\thetab_i^*$} if
gradients have been used, or as the Hessian of the GP, in case of
Bayesian Optimisation. The eigenvectors are computed using the function
\code{numpy.linalg.eig()}, and used as the axes of the
bounding box. Afterwards, the limits along the
eigenvectors are computed with
Algorithm~\ref{alg:region_construction}.

@@

\noindent
The function \code{fit_posterior} is a syntactic sugar for applying
\code{solve_problems} and \\ \code{estimate_regions} into a single
step. The function \code{visualize_region} can be used for plotting
the bounding box around the optimal point, when the parameter space is
one- or two-dimensional. The argument \code{i} is the index of the corresponding
optimisation problem i.e.\ $i<n_1$. \code{compute_eps} returns the
appropriate distance value $d_{i=\kappa}^*$ where
$\kappa = \lfloor quantile \cdot n \rfloor$ from the collection
$\{ d_i^* \} \forall i = \{1, \ldots, n\}$ where $n$ is the number of
accepted solutions. It can be used to automate the selection of the
threshold $\epsilon$, e.g.\ \code{eps=romc.compute_eps(quantile=0.9)}.

>>>>

\noindent
This method (a) draws the nuisance variables, (b) defines the
optimisation problems and (c) solves them using either a
gradient-based optimiser or Bayesian optimisation. These tasks are
completed sequentially, as shown in
Figure~\ref{fig:romc_overview}. The definition of the optimisation
problems is performed by drawing \code{n1} integer numbers from a
discrete uniform distribution \(u_i \sim \mathcal{U}\{1,
2^{32}-1\}\). Each integer \(u_i\) is the seed used in \pkg{ELFI}'s
random simulator. The seeds \(u_i\) are computationally analogous to
the random variables \(\vb_i\), that were defined in the previous
chapter; setting the \code{seed} eliminates all randomness of the
simulator transforming it to a deterministic function. Setting the
argument \code{use_bo=True}, chooses the Bayesian Optimisation scheme
for obtaining \(\thetab_i^*\). In this case, apart from obtaining the
optimal points \(\thetab_i^*\), we also fit a GP as a surrogate model
\(\hat{d}_i\). In this scenario, in the following steps,
\(\hat{d}_i(\thetab)\) replaces \(d_i(\thetab)\) as the distance
function.

@@

\noindent
This function helps the user decide which threshold \(\epsilon\) to
use. It plots a histogram of the distances at the optimal point
\(d_i(\thetab_i^*) : \{i = 1, 2, \ldots, n_1\}\) or \(\hat{d}_i^*\) in case
\code{use_bo=True}. The function accepts all keyword arguments and
forwards them to the underlying \code{matplotlib.pyplot.hist()} function; in
this way the user may customise some properties of the histogram, such
as the number of bins or the range of values.

@@

\noindent
This method constructs a bounding box around the optimal point
\(\thetab_i^* : i = 1, 2, \ldots, n_1\) following
Algorithm~\ref{alg:region_construction}. The Hessian matrix is
approximated based on the Jacobian
\(\hess_i = \jac_i^T \jac_i\)\footnote{The Jacobian matrix is computed
  on the output of the summary statistics
  \(\nabla_{\thetab} \Phi(M_d(\thetab, \vb_i))\) at \(\thetab_i^*\)} if
gradients have been used, or as the Hessian of the GP, in case of
Bayesian Optimisation. The eigenvectors are computed using the function
\code{numpy.linalg.eig()}, and used as the axes of the
bounding box. Afterwards, the limits along the
eigenvectors are computed with
Algorithm~\ref{alg:region_construction}.

@@

\noindent
The function \code{fit_posterior} is a syntactic sugar for applying
\code{solve_problems} and \\ \code{estimate_regions} into a single
step. The function \code{visualize_region} can be used for plotting
the bounding box around the optimal point, when the parameter space is
one- or two-dimensional. The argument \code{i} is the index of the corresponding
optimisation problem i.e.\ \(i<n_1\). \code{compute_eps} returns the
appropriate distance value \(d_{i=\kappa}^*\) where
\(\kappa = \lfloor quantile \cdot n \rfloor\) from the collection
\(\{ d_i^* \} \forall i = \{1, \ldots, n\}\) where \(n\) is the number of
accepted solutions. It can be used to automate the selection of the
threshold \(\epsilon\), e.g.\ \code{eps=romc.compute_eps(quantile=0.9)}.
